%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Antric K Nayakam}
\end{center}

 \begin{center}    
\small 904-339-5259 $|$
\href{mailto:antrickn@gmail.com}{\underline{antrickn@gmail.com}} $|$
\href{https://www.linkedin.com/in/antric-k/}{\underline{linkedin.com/in/antric-k/}} $|$
\small Coimbatore,TN.
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PSG Institute of Technology and Applied Research}{Coimbatore, TN}
      {CGPA 7.7 }{ Oct 2022 -- Present}
    \resumeSubheading
      {Viswaprakash Central School}{Thiruvanathapuram, KL}
      {AISSE 97\% }{ May 2021}
    \resumeSubheading
      {Sacred Heart International School}{Marthandam, TN}
      {ICSE 91\% }{ Mar 2019}
  \resumeSubHeadingListEnd



%-----------Experience-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {aXtr Labs}{Sept 2024 -- Oct 2024}
  {Web Development Intern}{Coimbatore, TN}
  \resumeItemListStart
    \resumeItem{Developed a modern and responsive website using \textbf{Next.js, Framer, and Tailwind CSS}, enhancing user engagement by \textbf{25\%} and achieving a \textbf{40\% faster page load time}.}
    \resumeItem{Designed \textbf{15+ custom animations and interactive components} with Framer and implemented Tailwind CSS’s utility-first approach to ensure consistency and reduce development time by \textbf{30\%}.}
  \resumeItemListEnd

      
\resumeSubheading
  {eSilicon Labs}{July 2024 –- Sept 2024}
  {Student Intern}{Coimbatore, TN}
  \resumeItemListStart
    \resumeItem{Developed a \textbf{decentralized IoT-based disaster alert system} using edge computing, enabling real-time detection of natural disasters and reducing response times by up to 40\%.}
    \resumeItem{Simulated disaster scenarios for \textbf{3 types of emergencies} (earthquake, flood, and fire) by creating Python-based sensor modules with \textbf{98\% accuracy} in detecting simulated events.}
    \resumeItem{Integrated \textbf{3 distinct alert mechanisms}, including SMS notifications to authorities (delivered within 10 seconds), text-to-speech (TTS) calls to emergency services.}
  \resumeItemListEnd


  \resumeSubHeadingListEnd




%-----------projects-----------
\section{Projects}
  \resumeSubHeadingListStart



      
      \resumeSubheading
  {Smart Grocery Management System}{Feb 2025 – Mar 2025}
  {IoT-Based Inventory Monitoring and Auto-Alert System}{}
\resumeItemListStart
  \resumeItem{Built a smart grocery container system using \textbf{ESP32} and \textbf{ultrasonic sensors} for real-time level tracking.}
  \resumeItem{Integrated with \textbf{ThingSpeak} for cloud-based data logging and visualization.}
  \resumeItem{Developed a backend script to send \textbf{WhatsApp alerts} when stock runs low.}
  \resumeItem{Designed a modular setup for scalable multi-container deployment with unique IDs.}
\resumeItemListEnd

      
    \resumeSubheading
      {ColaBoard}{May 2024 – Jun 2024}
      {Cloud-Based Task Manager Project}{}
      \resumeItemListStart
        \resumeItem{Designed and implemented a task management platform to streamline team collaboration, achieving an increase in productivity.}
        \resumeItem{Developed robust user authentication with role-based access control, ensuring secure data handling.}
        \resumeItem{Optimized database queries in MongoDB, reducing data retrieval time.}
    
      \resumeItemListEnd


      

    


  \resumeSubHeadingListEnd






%-----------Skill-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Area of Interest:} Operating Systems, Data Structures and Algorithms, Database Management Systems, Object Oriented Programming
    \item \textbf{Languages \& Frameworks:} Python, Java, C, Bash, JavaScript
    \item \textbf{Tools and Technologies:} Linux, Git, GitHub
\end{itemize}

%-----------Leadership-----------
\section{Leadership and Organizing Skills}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Lead, Google Developer Groups}{Oct 2024 - present}
      {Serving as the Web Development Team Lead for Google Developer Groups, PSG iTech}{}
    \resumeSubheading
      {IV Co-ordinator}{May 2024}
      {Organized an industrial visit to the SAP labs, Bangalore}{}
    
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
